Human Factors Influencing Visual Statistical Inference

### 2013-06-07 sociology_paper.tex
dots showing averages added to demographic factor plot
learning trend on time plot updated

\begin{figure}[htbp] 
   \centering
   \includegraphics[width=6.5in]{demographic_effect.pdf} 
   \caption{Boxplots of average time taken in log scale and proportion correct responses of all the lineups plotted for each demographic factor variables. None of the demographic factors appear to be statistically significant except India effect for proportion correct. Effect of graduate degree in proportion correct is also significant but is actually the India effect since, Most of the graduate degree holders are coming from India.}
   \label{fig:gender_country}
\end{figure}

@@

\begin{figure}[htbp] 
   \centering
   \includegraphics[width=6.5in]{learning_trend.pdf} 
   \caption{ Mean residuals of proportion correct obtained from the model \eqref{eqn:trend_response} fitted without attempt are plotted against attempt. A linear regression line through the points are shown. None of the slopes in these three experiments are statistically significant.}
   \label{fig:learning_trend}
\end{figure}

@@

\begin{figure}[htbp] 
   \centering
   \includegraphics[width=6.5in]{learning_trend_time.pdf}    
   \includegraphics[width=6.5in]{learning_trend_time_subject.pdf}    
   \caption{ Mean residuals of log(time taken) obtained from model \eqref{eqn:trend_time} fitted without covariate attempt plotted against attempt (above).  Subject-wise residuals of log(time taken) vs attempt (below). Linear regression lines are fitted through the points. For all the experiments the significantly downward slopes indicate that MTurk workers take less time as they progress through their attempts.}
   \label{fig:learning_trend_time}
\end{figure}

>>>>

\begin{figure}[htbp] 
   \centering
   \includegraphics[width=6.5in]{demographic_effect.pdf} 
   \caption{Boxplots of average time taken in log scale and proportion correct responses of all the lineups plotted for each demographic factor variables. The dots inside the box represents mean. None of the demographic factors appear to be statistically significant except India effect for proportion correct. Effect of graduate degree in proportion correct is also significant but is actually the India effect since, Most of the graduate degree holders are coming from India.}
   \label{fig:gender_country}
\end{figure}

@@

\begin{figure}[htbp] 
   \centering
   \includegraphics[width=6.5in]{learning_trend.pdf} 
   \caption{ Mean residuals of proportion correct obtained from the model \eqref{eqn:trend_response} fitted without attempt are plotted against attempt. Linear regression lines fitted through the points are shown. None of the slopes in these three experiments are statistically significant.}
   \label{fig:learning_trend}
\end{figure}

@@

\begin{figure}[htbp] 
   \centering
   \includegraphics[width=6.5in]{learning_trend_time.pdf}    
%   \includegraphics[width=6.5in]{learning_trend_time_subject.pdf}    
   \caption{ Mean residuals of log(time taken) obtained from model \eqref{eqn:trend_time} fitted without covariate attempt plotted against attempt. Linear regression lines are fitted through the points excluding the first attempt. For all the three experiments the downward slopes are statistically significant which indicates that MTurk workers take less time as they progress through their attempts.}
   \label{fig:learning_trend_time}
\end{figure}
